%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Researcher and Developer} % Job title
  {Engine Team, TeamT5} % Organization
  {Taipei, Taiwan} % Location
  {Oct. 2022 - present} % Date(s)
  {
    \begin{cvitems}
      \item {Shoving in my \textbf{first} commit right before hitting \textbf{5 hours} from onboarding}
      \item {Requested \textbf{4} merge requests in the \textbf{first week}}
      \item {Improved over \textbf{2x performance} of fundamental routine}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Operating System Teaching Assistant} % Job title
  {Department of Computer Science and Engineering, NSYSU} % Organization
  {Kaohsiung, Taiwan} % Location
  {Feb. 2021 - Jun. 2022} % Date(s)
  {Familiar with \textbf{Booting process} form \textbf{BIOS} and from \textbf{process}, \textbf{sched\_entity}}

  %---------------------------------------------------------
  \cventry
  {Club's Founding President} % Job title
  {Information Security Club, NSYSU} % Organization
  {Kaohsiung, Taiwan} % Location
  {Sep. 2019 - Jun. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {R\&D, Server Maintainer}
      \item {Teaching, Communicator}
      \item {Leaded club growing to \textbf{100 people}}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Network manager} % Job title
  {Campus Dormitory Promote Association (CDPA), NSYSU} % Organization
  {Kaohsiung, Taiwan} % Location
  {Sep. 2019 - Jun. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Network manager, R\&D}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Information Security Engineer Intern} % Job title
  {Telecom Technology Center} % Organization
  {Kaohsiung, Taiwan} % Location
  {Jun. 2019 - Aug. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Develop automatic apk vulnerability detection tool chain.}
      \item {Study static analysis tool which look for bugs in Java code.(SpotBugs)}
      \item {Familiar with \textbf{shell script}, \textbf{reverse engineering}}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
