\section*{Open Source Projects}

\begin{cvitem}
    \item \onelineproject{VMPilot} {https://github.com/25077667/vmpilot} 
    {is an advanced SDK employing post-quantum cryptography and compile-time/runtime obfuscation
    within a secure-by-design virtual machine to shield software from reverse engineering.}
    \item \onelineproject{Facebooc} {https://github.com/25077667/facebooc} 
    {is a comprehensive C-based proof of concept of a Facebook clone, showcasing
    end-to-end development from TCP socket programming to user interface design.}
    \item \onelineproject{scalable\_wg}{https://github.com/25077667/scalable\_wg}
    {is a compact PoC for a scalable WireGuard server, designed to support 
    over 5000 connections even on NT1000 hardware. It uses around 100 lines
    to efficiently load-balance and manage WireGuard tunnels.}
    \item \onelineproject{Sonar [C]ernel Commander (SCC)}{https://github.com/25077667/sonar-cernel-commander}
    {is an advanced Linux kernel module that specializes in syscall hooking and event logging. Designed 
    with performance and extensibility in mind.}
    \item \onelineproject{gcc (libstdc++)} {https://github.com/25077667/gcc/commit/715a82e84959c9493af1c925c109806f053a3358}
    {contributes about performance optimization for the GCC standard library, from $O(N^2)$ to $\Theta(N)$.(ongoing)}
    \item \onelineproject{spdlog (\textbf{19k, Gabime})}{https://github.com/Esri/spdlog/pull/3}
    {fixes an I/O inconsistency issue in the spdlog library.}
    \item \onelineproject{cpprestsdk (\textbf{7.5k, Microsoft})} {https://github.com/microsoft/cpprestsdk/pull/1746}
    {resolved a UTF-16 decoding issue, preventing overflow exceptions during serialization.}
\end{cvitem}

\section*{Non-Open Source Projects \small{(Personal research)}}

\begin{cvitem}
    \item \onelineprojectNoLink{Kernel Rootkit}{is a Linux kernel rootkit that hides kernel modules,
    zero-file-landing proccesses. Which is also a deep study of kprobes, signal handling, 
    input-event subsystem, kernel hacking etc.}

    \item \onelineprojectNoLink{DynamicLinkingLinux}{is a DLL-injection technique for Linux,
    injecting shared objects into running processes to modify their behavior. (developing)}
\end{cvitem}
